The Right Way to Search Evolving Graphs

### 2016-02-18 paper.tex
add BFS experiment table

To study evolving graphs and experiment with various graph types, we have
developed EvolvingGraphs.jl~\cite{zhang15}, a software package for the creation,
manipulation, and study of evolving graphs written in Julia~\cite{bkse12}.
It is freely available online at
\begin{center}
\url{https://github.com/weijianzhang/EvolvingGraphs.jl}
\end{center}
and available with the MIT ``Expat'' license. The package contains an implementation
of the evolving graph BFS.

%Julia is a high-level, high-performance dynamic programming language for technical
%computing.
% We make particular use of
% the parameterizable type system and multiple dispatch in Julia.
\texttt{MatrixList}, a data type in EvolvingGraphs.jl, represents an evolving graph
as a sequence of sparse matrices stored in compressed sparse column (CSC) format.
Many basic graph functions are also implemented for \texttt{MatrixList}.

>>>>

To study evolving graphs and experiment with various graph types, we have
developed EvolvingGraphs.jl~\cite{zhang15}, a software package for the creation,
manipulation, and study of evolving graphs written in Julia~\cite{bkse12}.
It is freely available online at
\begin{center}
\url{https://github.com/weijianzhang/EvolvingGraphs.jl}
\end{center}
and available with the MIT ``Expat'' license. The package contains an implementation
of the evolving graph BFS. \texttt{IntEvolvingGraph}, a data type in EvolvingGraphs.jl,
represents an evolving graph as adjacency lists. 
For a random (directed) \texttt{IntEvolvingGraph} with $5$ time stamps (each edge is included in the graph with probability $0.5$), 
Table \ref{tab:bfs} shows the time taken and 
the total number of bytes allocated of Algorithm \ref{alg:bfs}.
\begin{table}[h]
\centering
\begin{tabular}{c | c | c | c }
\hline
no. of nodes & no. of edges  & time(s) &  allocation(KB) \\\hline
           10               &        233               & 0.000180   & 43  \\
            15             &     510                  & 0.000285  &  73  \\
            20             &   961                   & 0.000431 &  115 \\
            25             &   1578                 & 0.000642 &   171 \\
            30             &  2174                  & 0.000819 &  268 \\
            35             &  3011                  & 0.001066 & 344
\end{tabular}
\caption{The time and the total number of bytes allocated for computing BFS
on a random evolving graph with 5 time stamps. Each row shows the
number of nodes, the number of edges, the time taken, and the memory requirements.}
\label{tab:bfs}
\end{table}
%Julia is a high-level, high-performance dynamic programming language for technical
%computing.
% We make particular use of
% the parameterizable type system and multiple dispatch in Julia.
\texttt{IntMatrixList}, a data type in EvolvingGraphs.jl, represents an evolving graph
as a sequence of sparse matrices stored in compressed sparse column (CSC) format.
We can convert an \texttt{IntMatrixList} to its corresponding block adjacency matrix
using the function \texttt{spmatrix}.
